Reproducibility in Plant Pathology

### 2020-04-20 README.rmd
Update README

This repository is organized as an R package. There is one R function,
`doi2bib()`, that is used in this repository, along with a bibliography file of
the articles that were examined that are located in `inst/extdata` directory. We
have used the R package structure to help manage dependencies, to take advantage
of continuous integration for automated code testing and for file organisation.

>>>>

This repository is organized as an R package. There are custom R functions, `doi2bib()`, `table_of_journals()` and `workflow_dia()` that are used in this repository, along with a bibliography file of the articles that were examined and the notes that are located in `inst/extdata` directory.
We have used the R package structure to help manage dependencies, to take advantage of continuous integration for automated code testing and for file organisation.
